Developing a Visual Studio Code Language Support Extension for the Snail Programming Language

### 2023-06-14 paper.tex
feat: mid section 4 backup

\subsection{LSP in Snail Language Support}

@@

\section{Snail Language Support package.json}

>>>>

\subsection{Language Servers in Snail Language Support}

In the Snail Language Support extension, we use a language server to validate snail files before runtime, checking for lexer and parser errors. With the extension enabled, VS Code is able to display lexer and parser errors, and highlight the relevant location of the error, before a developer runs the program themselves. This behavior is illustrated in Figure \ref{fig:dev-diagnostics}.

\begin{figure}
    \begin{subfigure}{0.45\textwidth}
        \begin{center}
            \includegraphics[width=\textwidth]{dev-no-diagnostics.png}
            \subcaption{Developing snail code without realtime error diagnostics can make it difficult to spot syntax errors.}
            \label{fig:dev-no-diagnostics}
        \end{center}
    \end{subfigure}
    \hspace{0.05\textwidth}
    \begin{subfigure}{0.45\textwidth}
        \begin{center}
            \includegraphics[width=\textwidth]{dev-with-diagnostics.png}
            \subcaption{With Snail Language Support, a developer can spot easily spot syntax errors and fix them before runtime.}
            \label{fig:dev-with-diagnostics}
        \end{center}
    \end{subfigure}
    \caption{Demonstrating the benefit of realtime error diagnostics provided in Snail Language Support.}
    \label{fig:dev-diagnostics}
\end{figure}

@@

\newpage
\section{Snail Language Support package.json}
